3 slides to convince you that it's endogenous TFP

### 2018-02-01 Latex/Basu_propositions/propositions.tex
Rolling averagen in basu's Presentation

Final goods firm (GE)
\begin{align*}
\max_{K^f_t(s), L^f_t(s), K^{IT}_t(s) } Y_t(s) =  & K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
 & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
 & \text{and} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
\end{align*}

>>>>

Final goods firm (GE)
\begin{align*}
\max_{K^f_t(s), L^f_t(s), K^{IT}_t(s) } Y_t(s) =  & K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
 & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
 &  \; A_t =  S_t \Psi_t (G(K^{IT}_t,K^{IT}_{t-1},\dots))^{\gamma} \\
 &  \; G(K^{IT}_t,K^{IT}_{t-1},\dots) = \zeta_1 K_t^{IT} + \zeta_2 K^{IT}_{t-1} + \dots \\
  & \text{and} \; \sum_{i=1}^{N} \zeta_i = 1
\end{align*}
